\documentclass[a4paper]{article}

\usepackage{fullpage}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[bottom=0pt, top=30pt, left=40pt, right=40pt]{geometry}

\pagestyle{empty}
\raggedright

\newcommand{\lineunder} { \vspace*{-8pt} \\ \hspace*{-18pt} \hrulefill \\ }
\newcommand{\header} [1] { {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}} \vspace*{-6pt} \lineunder }

\newcommand{\CC}{C\texttt{++}}
\newcommand{\CS}{C\texttt{\#}}

\setlist[itemize]{leftmargin=1em, topsep=1pt, itemsep=1pt, parsep=1pt}

\begin{document}

\begin{center}
	{\Huge \scshape {Mike Kot}} \\
    \href{mailto:to-job@myrrc.dev}{to-job@myrrc.dev} $\cdot$
    \url{https://myrrc.dev} \\
\end{center}

\header{Summary}

An experienced software engineer interested in both theoretical and practical aspects of building
high-load distributed systems, category theory, functional languages, and asynchronous programming.

\header{Experience}

\textbf{Senior software developer}, DoubleCloud \hfill Nov 2022 - Present \\
\textbf{Senior software developer}, Tinkoff \hfill May 2022 - Nov 2022 \\

\begin{itemize}
    \item Designed an in-house Gitlab CI replacement for Tinkoff ecosystem.
        Such CI would leverage analytics collection (including DORA metrics),
        add the ability to update pipeline steps in a centralized way (instead of per-project configuration),
        and provide a seamless developer experience for Tinkoff employees.
    \item Coordinated 12 people from 5 teams to develop the RFC and launch a public demo.
    \item Contributed to CI backend microservices in Golang.
\end{itemize}

\textbf{\CC\ developer}, Altinity \hfill June 2020 - Nov 2021 \\

\begin{itemize}
    \item Designed and implemented a ZooKeeper metadata restoration utility for ClickHouse
        distributed table engines. This utility minimized network overhead while restoring
        corrupted tables which, for some companies, resulted in a significant cost saving.
    \item Enhanced ClickHouse documentation by adding an automatically generated CMake flags
        reference which allowed ClickHouse developers to lower compilation time by at most
        four times.
    \item Introduced various improvements to ClickHouse's type system including possibility to
        multiply floating-point numbers by internal decimal format.
    \item Optimized query processing pipelines for various functions operating on dictionary-encoded
        types which lead to at most eleven times speedup.
    \item Participated in the development of "lightweight DELETEs" -- a fast way of deleting
        data from a possibly distributed table without mutations.
\end{itemize}

\textbf{\CC\ developer}, Rebus Capital \hfill May 2019 - June 2020 \\

\begin{itemize}
    \item Developed elements of a distributed system (cryptocurrency exchange),
        including web endpoints REST/WebSockets API, streaming engines, persistent storage,
        and the control module application coordinating other services.
    \item Implemented a Protobuf-like code generation tool converting internal schema format
        to JSON, C structures, and Swagger files.
\end{itemize}

\textbf{VR developer}, STEM Games \hfill Dec 2017 - Apr 2019 \\

\begin{itemize}
    \item Programmed various chemistry exploration levels for a VR chemistry
        laboratory, including "Chemical chains" and "Hydrolysis".
    \item Developed interfaces for chemistry supervisors (including multiple Unity3D interface
        extensions and a no-code levels constructor being
        an Unreal Engine Blueprints analog) which reduced the time spent on  levels creation
        by about seven times.
    \item Supervised an intern working on a journal of observations backend.
\end{itemize}

\header{Teaching experience}

\textbf{Student teacher, Curriculum designer}, Higher School of Economics 
\hfill Sep 2021 - Dec 2021 \\

\begin{itemize}
    \item Participated in the development of a new \CC\ curriculum for second-grade students
        that would prepare them for third-grade subjects and deepen their \CC\ knowledge.
        Prepared original assessments and held seminars.
    \item The course received \href{https://www.hse.ru/en/edu/courses/470902539}
        {"Best course for career development" and "Best course for new knowledge and skills"}
        awards.
\end{itemize}

\textbf{Calculus teaching assistant},
Higher School of Economics 
\hfill Sep 2018 - June 2020 \\

\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Mentored three groups of 25 students (first and second grade), raising student engagement
        in calculus; held consultations, checked assessments.
\end{itemize}

\header{Education}

\textbf{National Research University Higher School of Economics}, Moscow, Russia\\
Bachelor of Computer Science in Distributed Systems.

\textbf{Yandex School of Data Analysis}, Moscow, Russia\\
Discrete optimisation course, OS architecture course, Rust course, Concurrency course.

\header{Skills}
\begin{tabular}{@{} l l }
    Programming languages: & \CC \ (proficient); Python, Rust, Golang, Haskell, Lua (intermediate);
    OCaml, Scala (basic)\\
    Infrastructure: & Docker, Kubernetes (intermediate); Clang/LLVM (intermediate); \\
    Languages: & Russian (native), English (working proficiency).\\
\end{tabular}
\end{document}
